Reintroduction of resistant frogs facilitates landscape-scale recovery in the presence of a lethal fungal disease

### 2024-09-27 doc/manuscript/supplementary_information.qmd
Minor edits

---
format: 
  pdf:
    fig-pos: "H"
#format:
#   latex: 
#      cite-method: natbib
include-in-header:
  text: |
    \usepackage{blkarray}
    \usepackage{lineno}\linenumbers
include-before-body: 
  text: |
    \captionsetup{format=plain, labelfont=bf, labelsep=period}
editor: visual
editor_options:
  markdown:
    wrap: sentence
crossref: 
  fig-title: "**Supplementary Fig.**"
  fig-prefix: "Supplementary Fig."
  tbl-title: "**Supplementary Table**"
  tbl-prefix: "Supplementary Table"
bibliography: translocation.bib
csl: nature.csl
link-bibliography: true
---

@@

![**Average yearly survival probabilities of translocated versus naturally recruited adults.** Naturally recruited individuals were the result of reproduction by translocated frogs at each site. In contrast to Fig. 3, these are not survival probabilities from the first year following translocation, but instead represent averaged survival probabilities across multiple years and cohorts. Points are median estimates and error bars give the 95% uncertainty intervals around the estimates, accounting for yearly variation in survival probabilities. All estimates were derived using the mrmr package, and the methods for calculation are described in Supplemenary Information - Population viability modeling - Estimating model parameters. Source data are provided as a Source Data file. ](figures/compare_surv_probs.png){#fig-compare_surv_probs width="60%"}

>>>>

---
format: 
  pdf:
    fig-pos: "H"
#format:
#   latex: 
#      cite-method: natbib
include-in-header:
  text: |
    \usepackage{blkarray}
#    \usepackage{lineno}\linenumbers # Removed in final version
include-before-body: 
  text: |
    \captionsetup{format=plain, labelfont=bf, labelsep=period}
editor: visual
editor_options:
  markdown:
    wrap: sentence
crossref: 
  fig-title: "**Supplementary Fig.**"
  fig-prefix: "Supplementary Fig."
  tbl-title: "**Supplementary Table**"
  tbl-prefix: "Supplementary Table"
bibliography: translocation.bib
csl: nature.csl
link-bibliography: true
---

@@

![**Average yearly survival probabilities of translocated versus naturally recruited adults.** Naturally recruited individuals were the result of reproduction by translocated frogs at each site. In contrast to Fig. 3, these are not survival probabilities from the first year following translocation, but instead represent averaged survival probabilities across multiple years and cohorts. Points are median estimates and error bars give the 95% uncertainty intervals around the estimates, accounting for yearly variation in survival probabilities. All estimates were derived using the mrmr package, and the methods for calculation are described in Supplemenary Information - Population viability modeling - Estimating model parameters. Source data are provided as a Source Data file.](figures/compare_surv_probs.png){#fig-compare_surv_probs width="60%"}
